Contextual Identity: A Framework for Usable Privacy

### 2012-10-12 paper.tex
added buzz citation, expanded on contextual integrity ref

Barth et al.~ provide a formal model for contextual integrity of user
data~\cite{barth}. In contrast to this work, the contextual integrity model
focusses on data as principal rather than users.

@@

\section{Contextual identity violations}
\label{sec:examples}
\subsection{Redistributing information out of context}
Re-distributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals to the
user's activity stream.  Because of poor opt-out and lack of visibility into
what was being published, user outcry was immediate~\cite{mccarthy,nakashima}.
In December 2007, Google Reader exposed RSS feeds of user-marked news stories
to the user's Google Talk contacts\footnote{Google Talk contacts are everyone
with whom a user has chatted, which might include co-workers, supervisors, and
friends}. Although this feed was always public, prior to this launch it was not
discoverable, leading to a bad experience for many users~\cite{helft}. In
September 2012, Facebook imported old wall posts from 2008 into the new
Timeline interface.  Although wall posts were always visible from profile
pages, the new Timeline interface brought old wall posts (which users used to
treat as private messages, before the advent of ``Like'' and comment buttons)
to the attention of an audience that the user never intended~\cite{timeline}.

>>>>

Barth et al.~provide a formal model for contextual integrity of user
data~\cite{barth}. The contextual integrity model focusses on the flow of
personal information in terms of knowledge states held by agents rather than on
user identity, and works well for modeling privacy legislation and policy. In
contrast, this work's model provides a framework to understand users' ability
to represent which identity they want to use depending on context, and works
well for modeling software features.

@@

\section{Contextual identity violations}
\label{sec:examples}
\subsection{Redistributing information out of context}
Re-distributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals to the
user's activity stream.  Because of poor opt-out and lack of visibility into
what was being published, user outcry was immediate~\cite{mccarthy,nakashima}.
In December 2007, Google Reader exposed RSS feeds of user-marked news stories
to the user's Google Talk contacts\footnote{Google Talk contacts are everyone
with whom a user has chatted, which might include co-workers, supervisors, and
friends}. Although this feed was always public, prior to this launch it was not
discoverable, leading to a bad experience for many users~\cite{helft}. In
February 2010, Google Buzz launched, a product that
exposed the user's most frequent Gmail and Google Talk contacts and their
publicly available (through previously less discoverable) news and photos.  The
combination of exposing contacts (which could include abusive ex-husbands,
co-workers, and friends), as well as aggressively linking photos and news
items, resulted in a huge backlash~\cite{fugitivus,buzz}. In September 2012,
Facebook imported old wall posts from 2008 into the new Timeline interface.
Although wall posts were always visible from profile pages, the new Timeline
interface brought old wall posts (which users used to treat as private
messages, before the advent of ``Like'' and comment buttons) to the attention
of an audience that the user never intended~\cite{timeline}.
